\chapter*{Acknowledgments}
The task of writing a master's thesis is a demanding and extensive project which
I could not have been done without the support of many good people around me.
First of all, I want to thank my supervisors Henrik Andersen Sveinsson and
Anders Malthe-Sørenssen for the assistance in this thesis work. I am especially
grateful for the weekly meetings with Henrik and the inspiring discussion being
had as we unraveled the discoveries related to the topic of this thesis. I
remember that I initially asked for an estimate of how much time he had
available for supervision and the answer was something along the lines of
``There are no limits really, just send me an email and we figure it out''. This
attitude captures the main experience I have had working with Henrik and I am
profoundly grateful for the time and effort you have put into this project. I
hope that you do not regret said statement, too much, because I have certainly
been taken advantage of it. I also want to thank Even Marius Nordhagen for
technical support regarding the use of the computational cluster, in times when
the computer did exactly what it was told and was being silly. In that context,
I also want to acknowledge the University of Oslo (CCSE?) for making these
resources available. 

I would like to express my gratitude to all the parties involved in making it
possible for me to write my thesis from Italy. I am particularly grateful for
the flexibility shown by my supervisors and for the support of Anders
Kvellestad, who allowed me to work remotely as a group teacher. I would also
like to thank Scuola Normale Superiore for providing me with access to their
library.

I realize that it is a commonly used cliche to express gratitude for the support
of loved ones. However, I want to highlight the exceptional role played by my
fiancé, Ida. She deserves the main credit for helping me maintain a healthy
state of mind, and she has provided me with a solid foundation for a fulfilling
life that enables me to pursue secondary objectives, such as an academic career.
I look forward to spending the rest of my life with you. \\
\\
Throughout this thesis, I have used a formal ``we'' mainly as a customary habit
related to the formalities of scientific writing in a team. However, I have come
to the realization that this approach feels more appropriate since I have not
been working on this project alone. I have found support all the way from
colleagues and friends at the University of Oslo, to my family residing in
Denmark, and my life partner sleeping beside me every night here in Italy. They
constitute the ``good people around me'' who have made this thesis possible.

