\chapter{Summary}\label{chap:summary}

In this thesis, we have studied the nanoscale friction of a Kirigami graphene sheet
under the influence of load and strain using \acrshort{MD} simulations. We have
developed a numerical framework for generating diverse Kirigami designs which we have utilized to create a dataset for the frictional behavior depending on Kirigami pattern, strain, and loading. Our findings suggest that the frictional
behavior of a Kirigami sheet is highly dependent on the geometry of the pattern
and the strain conditions. We observed that the out-of-plane buckling can be
associated with a non-linear friction-strain curve which can be utilized to
demonstrate a negative friction coefficient in a system with coupled load and
strain. Moreover, we have investigated the possibility to use machine learning
on this dataset and attempted an accelerated search. Our findings imply that 
machine learning can be feasible for this approach,  additional data is required to
establish a more reliable foundation for a search for new Kirigami patterns. In this chapter, we will provide a summary of our findings and draw conclusions based on the results obtained. Finally, we will suggest some topics for further research.


\section{Summary and conclusions}

% 1: Design MD simulations
\subsection{Designing an MD simulation}
We have designed an \acrshort{MD} simulation for the examination of friction for
a graphene sheet sliding on a silicon substrate. The key system features were
the introduction of the pull blocks, defined as the end regions of the sheet
with respect to the sliding direction, which was utilized for applying normal
load and sliding the sheet. The pull blocks were made partly rigid and used to
employ a thermostat as well. Through an analysis of the friction forces retrieved from sliding simulations, we have established a standardized metric for kinetic friction. In particular, we measured the force exerted by the substrate on the full sheet, including the pull blocks, with respect to the sliding direction, and determined the kinetic friction as the mean value of the last half of the simulation. The uncertainties were estimated based on the fluctuations in the running mean. We found that the assessment of static friction was ambiguous for our simulation and did not pursue this further. From the analysis of the
force traces, friction force vs.\ time, we identify the friction behavior in our
simulation domain as being in the smooth sliding regime. This is attributed to the choice of a relatively high sliding speed (\SI{20}{m/s}) and infinitely stiff springs for the tethering of the sheet. This was supported by a demonstration of a transition to the stick-slip regime through the use of softer springs and a decrease in sliding speed. By conducting a more systematic investigation of the
effects of temperature, sliding speed, spring constant and timestep, we identified a set of default values based on numerical stability and computational cost. During this process, we aimed to select the variables that would maintain a relatively stable measured friction with moderate perturbations around these default values.
We found that friction increased with temperature which we attribute to being in
the ballistic sliding regime. In the absence of clear indications from the investigation regarding an appropriate temperature, we opted for the standard choice of room temperature, \SI{300}{K}. Furthermore, we found friction to increase with velocity as
expected, with some signs of phonon resonance at certain sliding speeds as well.
We chose a rather high velocity of \SI{20}{m/s} mainly for the consideration of
computational costs. For the spring constant, we found decreasing friction with
increasing stiffness of the springs. This is associated with the transition from
a stick-slip-influenced regime toward smooth sliding and can be attributed to an underlying change in commensurability. The choice of an
infinitely stiff spring was made from an assessment of the variation in friction with perturbations in the spring constant value. Finally, we
confirmed that a timestep of \SI{1}{fs} provides reasonable numerical stability.
However, based on fluctuations with timestep we find that the uncertainty in the
simulations might be higher than first estimated. For the non-strained Kirigami sheet, these fluctuations were on the order of $\pm \SI{0.017}{nN}$ for the evaluation of the kinetic friction.


% 2: Design Kirigami framework
\subsection{Generetig Kirigami patterns}
In order to investigate the effects of Kirigami design we have created a
numerical framework for generating various patterns. By defining an indexing
system for the hexagonal lattice structure we were able to define the Kirigami
designs as a 2D binary matrix for numerical implementation. We have selected two
macroscale designs, which we denote the \textit{Tetrahedron} and
\textit{Honeycomb} patterns, based on their ability to exhibit
out-of-plane buckling when subjected to strain. By digitalizing the designs to
match the hexagonal graphene lattice, we found that the characteristic design
features can be translated to the nanoscale, as we observed similar out-of-plane
buckling in \acrshort{MD} simulations. Through our numerical framework we were
able to create an ensemble of perturbed unique variations which yielded
approximately \num{135e3} and \num{2.025e6} unique configurations for the
Tetrahedron and Honeycomb patterns respectively. When considering the
possibility to translate the periodic patterns on the graphene sheet the number of possible patterns can be increased by approximately a factor of 100. To introduce some random design features, we have developed a framework for generating Kirigami patterns based on random walks. The framework includes mechanisms such as bias, avoidance of existing cuts, preference for maintaining a direction, and procedures for repairing the sheet for simulation purposes. In general, we found that the
capabilities of this numerical framework for generating Kirigami designs exceeded
our computational resources with regard to performing \acrshort{MD} simulation
under different loads and strains for each of the designs. In general, we found that the computational capacity of our numerical framework for generating Kirigami designs surpassed our available resources for conducting  \acrshort{MD} simulations under various load and strain for each design. Our \acrshort{MD}-based dataset only utilized a subset of configurations with 9660 data points based on 216 Kirigami configurations (Tetrahedron: 68, Honeycomb:
45, Random walk: 100, Pilot study: 3). Hence, we argue that the Kirigami generative framework can be valuable for further studies on an extended dataset.


% 3: Control friction using Kirigami
\subsection{Control friction using Kirigami}
We have investigated the frictional behavior of the Tetrahedron and Honeycomb
patterns in comparison to a non-cut sheet under various strains and loads.
Initially, we observed that straining the Kirigami sheets in a vacuum resulted
in an out-of-plane buckling. When adding the substrate to the simulation this
translated into a decreasing contact area with strain. We found the Honeycomb
sheet to exhibit the most significant buckling with a corresponding reduction of
relative contact area to approximately 43\%, whereas the non-cut sheet did not
produce any significant buckling in comparison. For the Kirigami sheets, we
found that friction initially increased with strain, which made for increasing
friction with decreasing contact area. As the strain continued to increase the
friction-strain curve exhibited highly non-linear trends with strong negative
slopes as well (see~\cref{fig:multi_stretch}). During the full strain, the
contact area was decreasing monotonically except for a slight increase just
before rupturing. These results contradict the asperity theory hypothesis of
decreasing friction with decreasing contact area, and we conclude that no clear
relationship between friction and contact area can be made. The non-cut sheet
did not show any significant dependency on the strain as both the friction and
the contact area remained constant with strain. Thus our findings suggest that a
changing contact area and the strain-induced friction effects might be
associated through an underlying mechanism connected to the buckling of the
sheet. We did find some independent effects from the introduciton of Kirigami
cuts before applying strain. We observed a small increase in friction between
the non-cut sheet and the Kirigami sheet, but this was one order of magnitude
lower than the effects associated with the strain in combination. Since the
strained non-cut sheet did not exhibit any significant effects from strain we
conclude that the independent effects from Kirigami cuts and tension in the
sheet cannot be regarded as a dominating mechanism for friction. When
considering the friction dependency with load, we generally found a weak
dependency corresponding to a friction coefficient on the order of
\num{e-4}--\num{e-5} even though we could not confirm any clear relationship.
This is best attributed to a superlubric state of the graphene sheet as seen in
other studies as well. The slope of the friction-load curve was not considerably
affected by the straining of the Kirigami sheet which led us to the conclusion
that strain-induced effects are dominant in comparison to any load-related
effects. In summary, we have found clear evidence that the friction in the
Kirigami sheet system is controlled by strain. 

When considering our findings in light of previous related results we find it
plausible that the governing mechanism for the observed friction effects is
related to commensurability. Since we have observed extremely low friction in
our system, we argue that the non-deformed sheet corresponds to an
incommensurable configuration. This is supported by the fact that we were not
able to lower the friction from the original starting point. Additionally, this
also aligns with the observation that the introduction of the non-strained
Kirigami designs increased friction slightly. Since some atoms were removed from
the lattice this can be hypothesized to relax the incommensurability to some
degree. When the Kirigami sheet buckles during stretching, it allows for a
considerable rearrangement of the atoms in contact with the substrate. Hence, it
may transition in and out of commensurable configurations, which could explain
the non-linear trend for the friction-strain curve. One way to test this
hypothesis is to reorientate the sheet in order to reach a commensurable start
configuration. Then we might find a transition from a commensurable to an
incommensurable case during the initial straining which would result in a
lowering in friction with respect to the starting point. 



% 4: Capture trends with ML
\subsection{Capturing trends in friction data with machine learning}
By utilizing the numerical framework for generating Kirigami design we have
created a \acrshort{MD}-based dataset for the frictional behavior depending on
Kirigami designs, load and strain. The dataset reveals some general correlations
with mean friction, such as a positive correlation to strain (0.77) and porosity
(0.60), and a negative correlation to contact area ($-0.67$). These results
align with the finding in the pilot study, suggesting that the change in
friction is associated with cuts in the sheet (porosity) and a changing contact
area. 

By defining the friction property metrics: $\min F_{\text{fric}}$, $\max
F_{\text{fric}}$, $\max \Delta F_{\text{fric}}$ and max drop (maximum decrease
in friction with strain), we investigated the top design candidates within our
dataset. From these results, we found no indication for the possibility to
reduce friction with the Kirigami approach since the non-cut sheet provided the
lowest overall friction. Furthermore, among the top candidates, we found that a
flat friction-strain profile is mainly associated with little decrease in the
contact area and vice versa. These observations are consistent with the results
of the pilot study and support the hypothesis that commensurability plays a key
role in governing the behavior of the system. In terms of the maximum
properties, we observed an improvement compared to the values obtained in the
pilot study, with the Honeycomb pattern exhibiting the highest scores. This
indicates that the data may be useful for optimizing these properties. 

For the machine learning investigation, we have implemented a VGGNet-16-inspired
convolutional neural network with a deep ``stairlike'' architecture:
C32-C64-C128-C256-C512-C1024-D1024-D512-D256-D128-D64-D32, for convolutional
layers $C$ with the number denoting channels and fully connected (dense) layers
$D$ with the number denoting nodes. The final model contains \num{1.3e7}
parameters and was trained using the ADAM optimizer for a cyclic learning rate
and momentum scheme. We trained the network for a total 1000 epochs while saving
the best model during training based on the validation score. The model
validation performance gives a mean friction $R^2$ score of $\sim 98\%$ and a
rupture accuracy of $\sim 96 \%$. However, we got lower scores for a selected
subset of the Tetrahedon ($R^2 \sim 88.7 \%$) and Honeycomb ($R^2 \sim 96.6$)
pattern based on the top 10 max drop scores respectively. The scores obtained
were lower, even though the selected configurations were partly included in the
training data and the hyperparameter selection favored the performance on this
selected set. Thus we conclude that these selected configurations, associated
with a highly non-linear friction-strain curve, represent a bigger challenge for
the machine learning prediction. One interpretation is that these involve the
most complex dynamics and perhaps that this is not readily distinguished from
the behavior of the other configurations which constitute the majority of the
data set. By evaluating the ability of the model to rank the dataset based on
property scores, we found that it was able to effectively represent the top
three scores for the maximum categories. However, the ranking for the minimum
friction property was lacking. We attribute this discrepancy to the fact that
this property requires a higher level of precision, which the model was not able
to achieve. To obtain a more accurate evaluation of the model's performance, we
generated a test set using \acrshort{MD} simulations for the random walk based
suggestions obtained from the accelerated search. The results showed a
significantly worse performance compared to the validation set, with a two-order
of magnitude higher loss and a negative $R^2$ score for the mean friction
property. The negative $R^2$ score suggests that the model's predictions were
worse than simply predicting the mean value of the true data.

However, by reevaluating the hypertuning and choosing solely on the basis of
validation loss, we still found poor results on the test set. This suggests that
the inadequate performance is not solely due to biased hypertuning but rather
because our original dataset did not sufficiently cover a diverse range of
Kirigami configurations to accurately capture the full complexity of its
frictional behavior. The validation scores indicate that the use of machine
learning is a feasible approach for addressing this problem, as we were able to
identify some general trends in the data. Nonetheless, from the test scores, it
is evident that further improvements to the dataset are necessary in order to
develop a reliable model.


% 5: Accelerated search
\subsection{Accelerated search}
Using the \acrshort{ML} model we performed two types of accelerated search. One
by evaluating the property scores of an extended dataset and another with the
use of the genetic algorithm approach. For the extended dataset search, we used
the developed pattern generators to generate \num{1.35e6} Tetrahedron,
\num{2.025e7} Honeycomb and \SI{10}{k} Random walk patterns. The search results
for the minimum friction property indicate a preference for low cut density or
low porosity. This aligns with the overall observation that the dataset does not
provide any suggestions to further reduction in friction, as the non-cut sheet
has the lowest friction. 

The search for the maximum properties resulted in some minor score increases but
the suggested candidates were mainly overlapping with the original dataset. By investigating the sensitivity to translations of the Tetrahedron and Honeycomb patterns, we observed significant variations in the model's predictions with only minor translations. This can be attributed to a physical dependency since these translations affect the edge of the sheet. However, given the poor model performance on the test set, we believe it is more likely that this variation is due to an insufficiency in the model caused by the limitations of the dataset.

In our investigation of the genetic algorithm approach, we used a starting population that was based on the results from the extended dataset accelerated search, as well as some randomly generated initializations with different porosity values. However, this approach did not provide any noteworthy
indication for new design structures worth more investigation. In general, the
initialization of the population itself proved to be a more promising strategy
than the genetic algorithm. We acknowledge that further effort could potentially yield useful results with the genetic algorithm approach. However, we believe that the current lack of promising results can be attributed to the uncertainty of the model which where the reason for not pursuing this any further.

By considering the Grad-CAM explanation method, we observed that the model predictions were often substantially reliant on the top and bottom edges of the Kirigami configurations. This was unexpected since these edges are not true edges but are connected to the pull blocks used in the simulation. Despite the model's uncertain predictions, we speculate that this may be due to the thermostat effects from the pull blocks. Therefore, we note this as a feature worth investigating in the simulations.



% 6: Negative friction coefficient
\subsection{Negative friction coefficient}
Based on our initial investigations of the Kirigami sheet, we have discovered a
highly non-linear friction-strain relationship. By proposing a linear coupling
between load and strain with ratio $R$, we find that these results suggest the
possibility to utilize the negative slope on the friction-strain curve to
achieve a negative friction coefficient. Based on the drop from top to bottom of
these curves, using the Tetrahedron $(7,5,1)$ and Honeycomb $(2,2,1,5)$ pattern
from the pilot study, we estimate that the average coefficient within this range
will be $-R\SI{12.75}{nN}$ for the Tetrahedron pattern and
$-R\cdot\SI{2.72}{nN}$  for the Honeycomb pattern.

To investigate this hypothesis, we conducted a simulation with a coupling
between load and sheet tension, mimicking a nanomachine attached to the sheet,
using the Kirigami configurations from the Pilot study. We observed that the non-linear behavior in the friction-strain curve also translated into a non-linear friction-load relationship for the coupled system. Additionally, we found that the Honeycomb pattern exhibited a non-linear strain-tension curve which resulted in an almost discontinuous increase in friction for the initial
increase in load. We attribute this feature to an unfolding process visually
confirmed from the simulation frames. For the coupled system with a
load-to-tension ratio of 6 we found regions in the friction-load curve with
significant negative slopes. By considering the maximum and minimum points for
such regions we estimated the average friction coefficient to be $-0.31$ in the
load range $F_N = [4.65, 6.55]$ nN for the Tetrahedron pattern and $-0.38$ in the
range $F_N = [0.71, 4.31]$ nN for the Honeycomb pattern. These results can be scaled by adjusting the load-to-tension ratio.

Based on our investigations, we have found that the combination of Kirigami cuts and strain has significant potential for controlling friction. Specifically, we have demonstrated that by enforcing a coupling between load and strain through tension, it is possible to achieve a negative friction coefficient. Therefore, we believe that this approach could be promising for developing novel friction-control strategies.




\section{Outlook}
% Active learning (Henrik)
% t-sne or similar to quanity the data distirbution
% Mention commensurability hyphothesis from summary

In this thesis, we have successfully shown that certain Kirigami designs exhibit non-linear behavior with strain. This discovery was done through a focus on the exploration of the effects of different designs. This invites further investigation of the underlying mechanisms behind this phenomenon. By considering one or two design, based on Tetrahedron and Honeycomb patterns, it would be valuable to investigate the effects on the friction-strain curve under various physical parameters. 

First of all, we suggest an investigation of how the friction-strain curve
depends on temperature, sliding speed, spring constant, and loads for an
increased range $F_N > 100 nN$. This is especially interesting in the context of
physical conditions leading to a stick-slip behavior since our study takes a
basis in smooth sliding friction. Moreover, it would be valuable to verify that
the choices for relaxation time, pauses, interatomic potentials and substrate
material are not critical for the qualitative observations. Especially the
Adaptive Intermolecular Reactive Empirical Bond Order (AIREBO) potential for the
modeling of the graphene sheet might be of interest. In this context, it might
also be useful to investigate the effects of excluding adhesion in the
simulations. In order to gain further insight into the role of commensurability
one could vary the scan angle as well. Since we suspect that our simulation
corresponds to a incommensurable superlubric state, certain scan angles is
hypothesized to yield higher friction. If the friction-strain curve is based on a commensurability effect this might yield qualitative different results and perhaps also allowing for a lowering of friction with strain. We might also consider investigating the friction-strain relationship under a uniform load to get insight into how the loading distribution effects the out-of-plane buckling and associated frictional effects.

Another topic worth studying is the relation to scale and edge effects. This includes an investigation of scaling effects, considering the ratio of the sheet to the edge, but also a translation of the sheet patterns to study the presence of any Kirigami-induced edge effects. The latter is motivated by the findings from the machine learning predictions. With this regard, we would also suggest a more detailed study of the effect of the thermostat in the pull blocks which is suggested to have a possibly importance when judging from the Grad-CAM analysis. 

For the machine learning approach, our findings suggest that the dataset is extended considerably. This can be done with respect to the aim of exploring Kirigami configurations as done in this thesis, but it can also be done for a single configuration under variation of some of the simulation parameters to support some of the above mentioned investigations. In that context, one could consider more advanced model architectures and machine learning techniques. If successful this would invite further studies of inverse design methods such as GAN or diffusion models. 

% \begin{itemize}
%   \item Investigate if the contact area is effecting the friciton non-linear by turning of friction force for atoms corresopnding to those that lift of from the sheet during the out-of-plane buckling. 
% \end{itemize}

% Things to include here
% \begin{itemize}
%   \item Could be valuable to spend more time on the validation of the MD simulations. How does material choice and potential effects the results. How realistic is the simmulations?
%   \item Are there any interesting approaches for compressed kirigami structures?
%   \item How does these results scale? I imagaind that the nanomachine systems should be applied in small units to avoid scaling problems, but in general I could spend way more time on the scaling investigation.
%   \item Since the normal force is applied at the pull blocks the normal force distribution changes from the sides more towards and even distribution as the sheet is put under tension (stretched). If we imagined a sheet for which the center part was either a different material or had some kind of pre-placed asperity on it, could we then exploit this force distirbution to get exotic properties as well? By studying this we might get a clearer understanding of what is the cause of my results. 
%   \item Possibility to study hysteresis effects. Maybe the frictional behvaiours change significantly through repeated cycles of stretch and relax. 
%   \item Try making substrate rigid to investigate the effect of this. 
%   \item Let the structure relax a bit longer perhaps, just to be sure that this does not affect the results. 
%   \item Extend load range
%   \item Try turning of adhesive forces to investigate the effects from adhesive forces. 
%   \item One way to investigate the importance of contact area is to turn of the friction force for of the atoms lifting away from the sheet during stretch. If this was purely a non-linear contact area dependency one would find the same results. If not we might point to the stress or other variables related to out-of-plane buckling.
%   \item Is the stretching effect caused by a commensurability effect. It does change where the pressure is applied. To test this one should look at the curves for other sliding direction. However, this would probably also predict similar differences in friction at a zero stretch state between different configuration which I do not think we get. However, since the stretched configurations put atom outside the hexagonal grid stucture it is per definition not achieveable to get those states for a non-strecthed sheet which support the idea of a commensurability effect.
%   \item How does it effect the results that we had a part on the pull blocks. 
%   \item Is there any effects from going over the same substrate multiple times. This is probably mainly interesting in the context of discussing velocity relationship where the substrate has less time to relax.
%   \item Interesting test could be to do the stretch curves with normal force applied on the whole sheet. The fact that the stretch provides tension might result in a better contact in the center... But the contact often goes down so maybe this was a silly idea.
%   \item Recap the suggestion to study translational of the patterns.
%   \item Could be interesting to optimize solely for the pop-up effect, i.e.\ through the biggest change in contact area. Maybe this is the key, since the succesfull pattern is choosen in that way. The correlation supports this, and the fact that the correlation is only about 60\% can be explained by the fact that the cases without considerable pop-up might not make any difference or perhaps that only some kinds of pop-up triggers the effect. 
%   \item Top and bottom edges showed to be of importance for the model prediction which leads to the idea of the thermostat in the pull blocks being important. This could be investigated in a further study. 
% \end{itemize}



% Thinks to do better in the simulation procedure:
% The graphene is first relaxed using conjugate gradient energy minimization and the relaxed within an NVT (fixed number of particles N , volume V and temperature T ) ensemble for 50 ps with non-periodic boundary conditions in all directions at a fixed temperature T = 4.2 K. The graphene is then stretched by moving the right and left edges at a constant strain rate of ∼ 0.005/ps which is slower than our previous work. \cite{PhysRevResearch.2.042006}

% Also to tru AIREBO which is also used in the above.